### 2025-08-26 manuscript/_figure1.qmd
additional text to MS, keywords analysis altered, figures revised

#### Classify order: Single author ----------
df$authortype <- 'Other'
df$authortype[df$author_order == 1] <- 'Other'
df$authortype[df$author_last == 1] <- 'Other'
df$authortype[df$author_single == 1] <- 'Single' # FOCUS
t<-table(df$authortype,df$Gender)
or1 <- effectsize::oddsratio(t) # 1.00
#print(or1)

#### Classify order: First author ----------
df$authortype <- 'Other'
df$authortype[df$author_order == 1] <- 'First'
df$authortype[df$author_last == 1] <- 'Other'
df$authortype[df$author_single == 1] <- 'Other' # Take out single authors from first authors!
t<-table(df$authortype,df$Gender)
or2 <- effectsize::oddsratio(t) # 1.41
#print(or2)

#### Classify order: Coauthor --------------
df$authortype <- 'Coauthor'
df$authortype[df$author_order == 1] <- 'Other'
df$authortype[df$author_last == 1] <- 'Other'
df$authortype[df$author_single == 1] <- 'Other' # Take out single authors from first authors!
t<-table(df$authortype,df$Gender)
or3 <- effectsize::oddsratio(t) # 1.00
#print(or3)

#### Classify order: Last -------------
df$authortype <- 'Other'
df$authortype[df$author_order == 1] <- 'Other'
df$authortype[df$author_last == 1] <- 'Last'
df$authortype[df$author_single == 1] <- 'Other' # Take out single authors from first authors!
t<-table(df$authortype,df$Gender)
or4 <- effectsize::oddsratio(t) # 0.73
#print(or4)

or <- rbind(or1,or2,or3,or4)
or$name<-c("Single","First","Coauthor","Last")
or<-dplyr::select(or,name,Odds_ratio,CI_low,CI_high)
#print(knitr::kable(or,digits = 2))

@@

output <- NULL
U<-levels(df$YEAR_5)
for (k in 1:length(U)){
  tmp<-dplyr::filter(df,YEAR_5==U[k])
  t <- table(tmp$authortype,tmp$Gender)
  output <- rbind(output,effectsize::oddsratio(t))
}
output$YearRange <- U
single <- data.frame(output)
#single

@@

output <- NULL
U<-levels(df$YEAR_5)
for (k in 1:length(U)){
  tmp<-dplyr::filter(df,YEAR_5==U[k])
  t <- table(tmp$authortype,tmp$Gender)
  output <- rbind(output,effectsize::oddsratio(t))
}
output$YearRange <- U
first <- data.frame(output)
#first

@@

U<-levels(df$YEAR_5)
output <- NULL
for (k in 1:length(U)){
  tmp<-dplyr::filter(df,YEAR_5==U[k])
  t <- table(tmp$authortype,tmp$Gender)
  output <- rbind(output,effectsize::oddsratio(t))
}
output$YearRange <- U
coauthor <- data.frame(output)
#coauthor

@@

U<-levels(df$YEAR_5)
output <- NULL
for (k in 1:length(U)){
  tmp<-dplyr::filter(df,YEAR_5==U[k])
  t <- table(tmp$authortype,tmp$Gender)
  output <- rbind(output,effectsize::oddsratio(t))
}
output$YearRange <- U
last <- data.frame(output)

@@

fig1 <- ggplot(annual2,aes(x=YearRange,y=Odds_ratio,color=Type,group=Type,shape=separator))+
  #facet_wrap(~TypeGroup,nrow = 2)+
  geom_hline(yintercept=1, linetype="dashed", color = "black") +
  geom_point(position = position_dodge(width = 0.4),show.legend=FALSE,size=3)+
  geom_errorbar(aes(ymin=CI_low,ymax=CI_high),width=0.2,position = position_dodge(width = 0.4))+
#  geom_line(alpha = 0.2,position = position_dodge(width = 0.4))+
  scale_shape_manual(values = c(22, 16)) +
  scale_color_brewer(name="Authorship\ntype",palette = "Set1",direction=-1) +
  xlab('Year range')+
  ylab('Female Authorship Odds Ratio (95%CI)')+
  theme_classic(base_size = 15)
print(fig1)

>>>>

#### Classify order: Single author ----------
df$authortype <- 'Other'
df$authortype[df$author_order == 1] <- 'Other'
df$authortype[df$author_last == 1] <- 'Other'
df$authortype[df$author_single == 1] <- 'Single' # FOCUS
# Explicit order of the rows and columns!
t <- table(
  factor(df$authortype, levels = c("Single", "Other")),
  factor(df$Gender,levels = c("female","male"))
)

or1 <- effectsize::oddsratio(t) # 0.90
#print(or1)

#### Classify order: First author ----------
df$authortype <- 'Other'
df$authortype[df$author_order == 1] <- 'First'
df$authortype[df$author_last == 1] <- 'Other'
df$authortype[df$author_single == 1] <- 'Other' # Take out single authors from first authors!
# t<-table(df$authortype,df$Gender)
# t
# Explicit order of the rows and columns!
t <- table(
  factor(df$authortype, levels = c("First", "Other")),
  factor(df$Gender,levels = c("female","male"))
)
or2 <- effectsize::oddsratio(t) # 1.41
#print(or2)

#### Classify order: Coauthor --------------
df$authortype <- 'Coauthor'
df$authortype[df$author_order == 1] <- 'Other'
df$authortype[df$author_last == 1] <- 'Other'
df$authortype[df$author_single == 1] <- 'Other' # Take out single authors from first authors!
# Explicit order of the rows and columns!
t <- table(
  factor(df$authortype, levels = c("Coauthor", "Other")),
  factor(df$Gender,levels = c("female","male"))
)

or3 <- effectsize::oddsratio(t) # 1.00
#print(or3)

#### Classify order: Last -------------
df$authortype <- 'Other'
df$authortype[df$author_order == 1] <- 'Other'
df$authortype[df$author_last == 1] <- 'Last'
df$authortype[df$author_single == 1] <- 'Other' # Take out single authors from first authors!
t <- table(
  factor(df$authortype, levels = c("Last", "Other")),
  factor(df$Gender,levels = c("female","male"))
)

or4 <- effectsize::oddsratio(t) # 0.73
#print(or4)

or <- rbind(or1,or2,or3,or4)
or$name<-c("Single","First","Coauthor","Last")
#_or<-dplyr::select(or,name,Odds_ratio,CI_low,CI_high)
#_print(knitr::kable(or,digits = 2))

@@

output <- NULL
U<-levels(df$YEAR_5)
for (k in 1:length(U)){
  tmp<-dplyr::filter(df,YEAR_5==U[k])
  t <- table(
    factor(tmp$authortype, levels = c("Single", "Other")),
    factor(tmp$Gender,levels = c("female","male"))
  )
  output <- rbind(output,effectsize::oddsratio(t))
}
output$YearRange <- U
single <- data.frame(output)
#single

@@

output <- NULL
U<-levels(df$YEAR_5)
for (k in 1:length(U)){
  tmp<-dplyr::filter(df,YEAR_5==U[k])
  t <- table(
    factor(tmp$authortype, levels = c("First", "Other")),
    factor(tmp$Gender,levels = c("female","male"))
  )
  output <- rbind(output,effectsize::oddsratio(t))
}
output$YearRange <- U
first <- data.frame(output)
#first

@@

U<-levels(df$YEAR_5)
output <- NULL
for (k in 1:length(U)){
  tmp<-dplyr::filter(df,YEAR_5==U[k])
  t <- table(
    factor(tmp$authortype, levels = c("Coauthor", "Other")),
    factor(tmp$Gender,levels = c("female","male"))
  )
  output <- rbind(output,effectsize::oddsratio(t))
}
output$YearRange <- U
coauthor <- data.frame(output)
#coauthor

@@

U<-levels(df$YEAR_5)
output <- NULL
for (k in 1:length(U)){
  tmp<-dplyr::filter(df,YEAR_5==U[k])
  t <- table(
    factor(tmp$authortype, levels = c("Last", "Other")),
    factor(tmp$Gender,levels = c("female","male"))
  )
  output <- rbind(output,effectsize::oddsratio(t))
}
output$YearRange <- U
last <- data.frame(output)

@@

custom_palette <- brewer.pal(n = 4, name = "Set1")
custom_palette<-c(custom_palette[4],custom_palette[1:3])

fig1 <- ggplot(annual2,aes(x=YearRange,y=Odds_ratio,color=Type,group=Type,shape=separator))+
  #facet_wrap(~TypeGroup,nrow = 2)+
  geom_hline(yintercept=1, linetype="dashed", color = "black") +
  geom_point(position = position_dodge(width = 0.4),show.legend=TRUE,size=3)+
  geom_errorbar(aes(ymin=CI_low,ymax=CI_high),width=0.2,position = position_dodge(width = 0.4))+
#  geom_line(alpha = 0.2,position = position_dodge(width = 0.4))+
  scale_shape_manual(name="Authorship\ntype",values = c(22, 16),guide = "none") +
  scale_color_manual(name="Authorship\ntype",values=custom_palette) +
  xlab('Year range')+
  ylab('Female Authorship Odds Ratio (95%CI)')+
  theme_classic(base_size = 15)
print(fig1)

### 2025-08-26 manuscript/_figure2.qmd
additional text to MS, keywords analysis altered, figures revised

#### classify order: First author -------
df$authortype <- 'Other'
df$authortype[df$author_order == 1] <- 'First'
df$authortype[df$author_last == 1] <- 'Other'
#table(df$authortype,df$Gender)

output <- NULL
U<-levels(df$author_N_cropped)
for (k in 2:length(U)){
  tmp<-dplyr::filter(df,author_N_cropped==U[k])
  t <- table(tmp$authortype,tmp$Gender)
  output <- rbind(output,effectsize::oddsratio(t))
}

@@

#### classify order: Coauthor ----------
df$authortype <- 'Coauthor'
df$authortype[df$author_order == 1] <- 'Other'
df$authortype[df$author_last == 1] <- 'Other'
#table(df$authortype,df$Gender)

output <- NULL
U<-levels(df$author_N_cropped)
for (k in 3:length(U)){
  tmp<-dplyr::filter(df,author_N_cropped==U[k])
  t <- table(tmp$authortype,tmp$Gender)
  output <- rbind(output,effectsize::oddsratio(t))
}

@@

#### classify order: Last ----------
df$authortype <- 'Other'
df$authortype[df$author_order == 1] <- 'Other'
df$authortype[df$author_last == 1] <- 'Last'

output <- NULL
U<-levels(df$author_N_cropped)
for (k in 2:length(U)){
  tmp<-dplyr::filter(df,author_N_cropped==U[k])
  t <- table(tmp$authortype,tmp$Gender)
  output <- rbind(output,effectsize::oddsratio(t))
}

>>>>

#### classify order: First author -------
df$authortype <- 'Other'
df$authortype[df$author_order == 1] <- 'First'
df$authortype[df$author_last == 1] <- 'Other'
df$authortype[df$author_single == 1] <- 'Other'
#table(df$authortype,df$Gender)

output <- NULL
U<-levels(df$author_N_cropped)
for (k in 2:length(U)){
  tmp<-dplyr::filter(df,author_N_cropped==U[k])
#  t <- table(tmp$authortype,tmp$Gender)
  t <- table(
    factor(tmp$authortype, levels = c("First", "Other")),
    factor(tmp$Gender,levels = c("female","male"))
  )
  output <- rbind(output,effectsize::oddsratio(t))
}

@@

#### classify order: Coauthor ----------
df$authortype <- 'Coauthor'
df$authortype[df$author_order == 1] <- 'Other'
df$authortype[df$author_last == 1] <- 'Other'
df$authortype[df$author_single == 1] <- 'Other'
#table(df$authortype,df$Gender)

output <- NULL
U<-levels(df$author_N_cropped)
for (k in 3:length(U)){
  tmp<-dplyr::filter(df,author_N_cropped==U[k])
#  t <- table(tmp$authortype,tmp$Gender)
  t <- table(
    factor(tmp$authortype, levels = c("Coauthor", "Other")),
    factor(tmp$Gender,levels = c("female","male"))
  )

  output <- rbind(output,effectsize::oddsratio(t))
}

@@

#### classify order: Last ----------
df$authortype <- 'Other'
df$authortype[df$author_order == 1] <- 'Other'
df$authortype[df$author_last == 1] <- 'Last'
df$authortype[df$author_single == 1] <- 'Other'

output <- NULL
U<-levels(df$author_N_cropped)
for (k in 2:length(U)){
  tmp<-dplyr::filter(df,author_N_cropped==U[k])
  #t <- table(tmp$authortype,tmp$Gender)
  t <- table(
    factor(tmp$authortype, levels = c("Last", "Other")),
    factor(tmp$Gender,levels = c("female","male"))
  )

  output <- rbind(output,effectsize::oddsratio(t))
}
